### 2021-12-10 thesis/tex/ICintro.tex

\section{Neutrino detection}
\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
gets its flavor and energy changed. In NC interactions, no flavor change can occur, so the fermion leaves with increased energy.
This fermion is then directly or indirectly detected, 
and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

@@

The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}.
The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over the azimuthal direction and solar minimum/maximum. 
The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
from the table for clarity. 
We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons do not decay into $\nt$. Thus, we never have to use probabilities in the form 
$P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
Interpolating the data yields makes us capable of approximating all four necessary fluxes for a given true energy and true zenith.
The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. This is due to the 
very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
equal. First, the difference in the density profiles introduces wildly different matter effects. 
Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.

>>>>

\section{Neutrino detection}
\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}
% TODO: Write down CC NC equations after 1st paragraph, using N and N’ (N’ can be shower etc).
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
gets its flavor and energy changed. In NC interactions, no flavor change can occur, so the fermion leaves with increased energy.
This fermion is then directly or indirectly detected, 
and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

@@

The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}.
The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over the azimuthal direction and solar minimum/maximum. 
The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
from the table for clarity. 
We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons do not decay into $\nt$. Thus, we never have to use probabilities in the form 
$P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
Interpolating the data yields makes us capable of approximating all four necessary fluxes for a given true energy and true zenith.
The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. 
% This is due to the 
% very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
% large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
% small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
% equal. 
% First, the difference in the density profiles introduces wildly different matter effects. 
% Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
% overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.

### 2021-12-10 thesis/tex/introduction.tex
Corrected

In Chapter~\ref{ch:ic}, we present an experimental procedure used to observe signals from neutrinos originating from cosmic ray interactions in the atmosphere of the Earth. 
Furthermore, present the two present Antarctic neutrino detectors: IceCube and DeepCore.
We also summarize a proposed detector upgrade: Precision IceCube Next Generation Upgrade (PINGU), which we will use as a forecast in our analysis.

@@

Finally, Chapter~\ref{ch:results} contains the result from our two separate extensions of the Standard Model.
In Section~\ref{sec:sterileResults} we present our findings for the sterile neutrino and compare those with literature. 
In Section~\ref{sec:nsiResults}, we present new constrained bounds on the NSI parameters by combining our results for IceCube, DeepCore, and PINGU.

>>>>

In Chapter~\ref{ch:ic}, we present an experimental procedure used to observe signals from neutrinos originating from cosmic ray interactions in the atmosphere of the Earth. 
Furthermore, two Antarctic neutrino detectors are introduced: IceCube and DeepCore.
We also summarize a proposed detector upgrade: Precision IceCube Next Generation Upgrade (PINGU), which we will use as a forecast in our analysis.

@@

Finally, Chapter~\ref{ch:results} contains the result from our two separate extensions of the Standard Model.
In Section~\ref{sec:sterileResults} we present our findings for the sterile neutrino and compare those with literature. 
In Section~\ref{sec:constraining}, we present new constrained bounds on the NSI parameters by combining our results for IceCube, DeepCore, and PINGU.
